### 2021-05-12 docs/manuscript/PLOS-MSc-Thesis.tex
Add link to Fig 5 when mentioning topology 420

The correlation between the complexity index of a topology and its abundance
indicates that networks with simpler designs are more robust to changes in
interaction parameters and that more complex networks are less robusts. For
example, topology number 420, which presents high complexity, was one of the
topologies with lower abundance and was disconnected from all other topologies
in the two-step neighbors in the neutral network.

>>>>

The correlation between the complexity index of a topology and its abundance
indicates that networks with simpler designs are more robust to changes in
interaction parameters and that more complex networks are less robusts. For
example, topology number 420 \hil{(Fig}~\ref{fig:2neut-net}), which
presents high complexity, was one of the
topologies with lower abundance and was disconnected from all other topologies
in the two-step neighbors in the neutral network.
